r5r: Rapid Realistic Routing with R5 in R

### 2020-08-25 r-package/paper2020/paper2020.Rmd
tests with skip_on_cran and skip_on_travis

This article presents **r5r**, a new open-source `R` package for rapid 
realistic routing on multimodal transport networks.

@@

@@

@@

>>>>

...

@@

Section to demonstrate how to use the core functions of the package. We can use 
our intro vignette as a starting point and build from there with more the analysis
of larger data sets, include couple more data visualization of results and emphasize
the results of multiple route alternatives.

@@

Conveyal for R5

@@

#> Rafa's notes
#> jean: #>-  mass of assumptions regarding decision-making and routing (Miller, 2018). 
#>Haugen, 2011; Schwanen, 2008
#>
#>Miller, E.J., 2018. Accessibility: measurement and application in transportation planning. Transp. Rev. 38, #>551–555. https://doi.org/10.1080/01441647.2018.1492778
#>
#>This article presents **r5r**, a new open-source `R` package for rapid 
#>realistic routing on multimodal transport networks.
